EDIpack2: interoperable Lanczos-based solver for generic quantum impurity problems

### 2025-05-16 05_examples.tex
Updates from Overleaf

>>>>

\subsection{Holstein model on the Bethe lattice (Fortran)}

One of the features introduced in \NAME is the possibility of treating local phonons in the superconductive case (i.e. \textbf{ed\_mode=superc} ). In this example we show how to get the normal and superconductive solutions of the Holstein model on the Bethe lattice within DMFT. The phononic and electron-phonon part of the Holstein hamiltonian at half-filling for particle-hole symmetric density of states like in the Bethe lattice reads:
\begin{equation} \label{eqex:H_Holstein}
    H_{int} = \sum_i \Big[\omega_0 b^\dagger_i b_i + g(b^\dagger_i + b_i)\sum_{\sigma}(c^\dagger_{i\sigma}c_{i\sigma} -\frac{1}{2})\Big]
\end{equation}

This interaction in two limits takes two simpler forms, for $\omega_0 \rightarrow \infty$ with $g^2/\omega_0=\lambda$ constant, also known as anti-adiabatic limit, the interaction becomes a Hubbard attraction:
\begin{equation}
    H_{int} \overset{ \omega_0 \rightarrow \infty}{ \longrightarrow } -\frac{\lambda}{2} \sum_i \Big[\sum_\sigma(c^\dagger_{i\sigma}c_{i\sigma} -\frac{1}{2}) \Big]^2
\end{equation}

Meanwhile in the opposite limit, $\omega_0 \rightarrow 0$ with $g^2/\omega_0=\lambda$ constant, also known as adiabatic limit, the phonons are condensed and the creation/annihilation operators can be considered as a scalar number to be determined self-consistently. In that case the interaction at equation \eqref{eqex:H_Holstein} for uniform solution vanishes and one recovers the non-interacting limit.

THE FOLLOWING MAYBE IN THE E-PH SECTION

The phonon's frequency is passed to the \NAME program via the variable W0\_PH to be read from the input file. The displacement field acting on the phonon is passed thorugh the variable A\_PH from the input file. The electron-phonon coupling matrix $g_{\alpha \beta}$ instead can be passed in two different ways. If the matrix is diagonal ($g_{\alpha \beta} = g_\alpha \delta_{\alpha \beta}$), from the input file one can simply write in order the values $g_\alpha$ in the variable G\_PH. For any general shape one can pass to the input file a GPHfile variable containing the name of the file storing the $g_{\alpha \beta}$ array in Fortran style.
If GPHfile=NONE the matrix $g_{\alpha \beta}$ is read from the variable G\_PH, else it is read from the GPHfile.

In the following we show for a fixed value of $\lambda=2$ the adiabatic to anti-adiabatic crossover for the uniform solution of the Holstein problem.

PLOT docc vs W0, superc and normal
PLT delta vs w0, superc

### 2025-05-16 edipack2.tex
More relevant content
Important stuff part 3
Important changes part 4
Updates from Overleaf

\usepackage{bbold}
\def\11{\mathbb{1}}
\def\00{\mathbf{0}}
\def\NAME{{\rm EDIpack2}\xspace}

@@

\section{Appendix A: Monicelli interface}

@@

Come {\tt https://github.com/lcrippa/prematurata\_la\_dmft} per esempio. No dico, mi porga il file {\tt bagaglio.cpp}. Le vede le funzioni? Lo vede che interfacciano gli array, non supportati da Monicelli, e prematurano anche?
Ora io le direi, anche con il rispetto per l'autorità, anche solo le due parole come install Monicelli from {\tt https://github.com/esseks/monicelli.git} and run Make which compiles and links the main file {\tt hm\_bethe.mc}, per esempio. Basta così, mi seguano nel programma di test. No no, Attenzione: loop dmft completo supportato secondo la ref. \cite{EDIpack} abbia pazienza. Se no, plotta i dati, anche un pochino Green's function e Self-energy in prefettura. Senza contare che {\tt prematurata\_la\_dmft} ha perso i contatti con il tarapia tapioco, dopo.

>>>>

\usepackage{bbold}
\def\11{\mathbb{1}}
\def\00{\mathbf{0}}
\def\NAME{{\rm EDIpack2}\xspace}
\newcommand{\shortrightarrow}{\mathrel{\mkern3mu\rightarrow\mkern}}

@@

\section[appA]{Appendix A: Monicelli interface
\footnote{Monicelli is an esoteric programming language based on the LLVM toolchain. It is written in C++ and offers wrappers for the basic types and operations thereof. The syntax replicates a cultural italian phenomenon known as ``supercazzola", a rambling nonsensical discourse which gives the false impression of carrying an actual meaning. As an interoperability showcase we present a fully functioning DMFT code for the Bethe lattice written in Monicelli. It requires a minimal C++ interface to handle arrays, complex numbers and properly interfacing the EDIpack functions. }}

@@

Come {\tt https://github.com/lcrippa/prematurata\_la\_dmft} per esempio. No dico, mi porga il file {\tt bagaglio.cpp}. Le vede le funzioni? Lo vede che interfacciano gli array, non supportati da Monicelli, e prematurano anche?
Ora io le direi, anche con il rispetto per l'autorità, anche solo le due parole come install Monicelli from {\tt https://github.com/esseks/monicelli.git} and run Make which compiles and links the main file {\tt hm\_bethe.mc}, per esempio. Basta così, mi seguano nel programma di test. No no, Attenzione: loop dmft completo supportato secondo la ref. ~\cite{Georges1996RMP} abbia pazienza. Se no, plotta i dati, anche un pochino Green's function e Self-energy in prefettura. Senza contare che {\tt prematurata\_la\_dmft} ha perso i contatti con il tarapia tapioco, dopo.
